Teaching a Class to Grade Itself using Game Theory

### 2013-09-20 Primes Write up.tex
Finished up my edits to results and such. Not much left

\documentclass[12pt, Arial]{article}   	
\title{Teaching a Class to Grade Itself using Game Theory}
\author{Nick Kaashoek and William Wu}
\date{\today}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{cite}
\usepackage{graphicx}
\setlength{\parindent}{15pt}
\begin{document}
\maketitle
\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole. Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started in May of 2012~\cite{canmoocsreducecc}. However, the MOOC's main importance comes from its scalability. MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: By the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofmoocs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

@@

\section{Materials and Methods}
\subsection{The Scenario}
In our trying to find a solution to the professor's problem, we consider the case of a single assignment. To apply them to an entire class, simply apply them to each assignment. In such a ``round''of grading, there are $n$ students, who each bring one ungraded paper to the professor. These ungraded papers are like the input for a function. Each of these papers, $i$ has an objective score $o_i\mid 0<o_i<100$. This is the score the professor would give out. Our mechanism then has the students grade the papers in a clever way and output the grades. We identify the students by an index $i$ from $1$ to $n$ and the professor as index $0$.
\subsection{Assumptions}
To create the models that are used to predict the behavior of the students, we use a set process every each time. To begin with, we create a set of assumptions. These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades. This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model. The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side. To begin with, a simple set of assumptions was created:
\begin{enumerate}
	\item Students want good grades
 	\item Doing work makes students unhappy
  	\item Students want to be happy
 	\item Students only care about their final happiness
  	\item The happiness of a student is only affected by their grade and the amount of work they do
\end{enumerate}
However, we wanted to create a mathematical solution, so these assumptions need to be changed into math terms. The result of this is as follows:
\begin{enumerate}
  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
  \item Students can grade others' work accurately (i.e they can find $o_i$) but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
  \item Students want to maximize their final happiness, expressed as $H(g)-W$
  \item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting x and y each with 50 percent chance, gives a happiness of 7.5).
  \item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It doesn't depend on the score of others
\end{enumerate}

@@

One advantage of this is that we can now address the fact that the above set of assumptions is rather simple and unrealistic, for instance assuming that every student is a perfect grader.
%Repeat above corrections%

\section{Discussion}
With this research, the goal was to create a mechanism that fulfilled our two goals; incentivizing students to play the ``game''the way they were meant to, and to efficiently and effectively grade the assignments of these students. Although our mechanisms are not truly realistic, the significance of them cannot be denied. The mechanisms created by the end of the research came very close to realism, with only one factor missing, and could still be implemented in a classroom environment where all students are capable of grading others assignments efficiently.

@@

Human judgment has always been superior to that of a machine, and this research continues to support that idea. As powerful as automated grading can be in practice, when it comes to theory, peer grading is simply more efficient. This means that with the right mechanism, such as the ones proposed by this research, so, in practice peer grading should be superior to automated grading. All in all, this research has opened doors for game theorists to make improvements to current grading schemes, and also provides mechanisms that are a distinct improvement over current peer and automated grading systems.
\section{Results}
%[Note from Matt and Christos: Add some discussion about the benchmark: why do you care about workload? Why do you care about accurate grades? If you just care about workload, give everyone 100. If you just care about grades, have the professor grade everything. Need to consider both to properly model the problem.]
Once the rules and assumptions have been defined and the benchmark determined, different grading mechanisms can be created and tested. This is where mechanism design and game theory comes into play. Mechanism design is used to create a system that satisfies a set of constraints and achieves a certain purpose. Then, game theory is used to mathematically predict student behavior to benchmark such a system. Starting from the simplest and most obvious approaches, various mechanisms were created, tested, and refined upon in an iterative process that spanned several months. The end result is fairly complete, although there are still questions to be answered in future work.

\section{The Calibration Mechanism}
\label{sec:calibration}

This mechanism is quite unrealistic, but not by such a degree that it is unimaginable. Because of this, it was possible to create a perfect solution if the problem took place in this situation.

\subsection{Mechanism}
In the mechanism, the professor grades one paper, called \emph{X}. The professor then distributes all the student's papers randomly among the students, while making sure that no student receives his or her own paper. Every student is also given a copy of \emph{X}.

The professor then tells the students that ``Out of the two papers you were given, one of them has been graded by me, and the other hasn't. If you fail to give the correct grade for the one I graded, then you will receive a 0.'' The students then go about their business grading the papers, and individually report the grades they gave out to the professor. Then, just like the professor promised, if the students graded the pre-graded, or \emph{calibrated} paper incorrectly, then that grader gets a 0 on the assignment. If they graded correctly, their assigned grade is guaranteed to be at least some minimum value.

See figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.

\subsection{Why it Works}
G is the maximum of \{ some minimum value, the assigned grade \}.

The happiness of one student grading one paper is equivalent to $$\frac{H(G)+H(0)}{2}-1$$ Because the students have a 0.5 chance of getting a 0, and a one-half chance of getting G.

If they grade both papers, their happiness will be equal to $$H(G)-2$$Because they spent two units of energy, and are guaranteed to get G.

If they grade neither then the happiness will be $$H(0)$$ Because they automatically get a 0, but spend no energy.

This means that if $H(G) - 2 > H(0)$, then student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, he or she would choose a minimum value such that $H(G) > H(0) + 2$.
\subsection{Results}
The teacher expends one unit of effort, and the students each spend 2, as long as the teacher set the minimum value high enough.
Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
This means that the maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
The means that the value of the objective function in this case is 4, a very low value, which shows how effective this solution is.

\subsection{Problems}
The goal for this mechanism was to make it more realistic while still making it simple to understand, and have a simply solution that would be easy for students to understand. There is now a mechanism that works very well in an unrealistic scenario, so we moved on to a new mechanism.

\section{Improved Calibration Mechanism}
The major change made in this mechanism was one to assumption number 11. Now assumption 11 reads as follows:
\emph{All students are able to communicate with each other}

This provides a very different scenario than the original mechanism, because now students will be able to figure out which papers are calibrated. However, it would be better to try and generalize the previous solution and apply it to the new mechanism, which leads to the following scheme.

\subsection{Mechanism}
The first attempt to apply a solution to this mechanism was a near carbon copy of the previous scheme.
The class is arranged in a virtual circle, where every student grades the papers of the \emph{k} students to the right of them. The professor also grades every \emph{kth} paper starting from some random point in the circle. If a student mis-grades the calibrated paper, they get a 0, otherwise they get the maximum of their objective score and the minimum value from the previous mechanism.

\subsection{Why it Works}
In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other. As such, there are 3 options for the students.

1) They can grade 0 papers, giving them a happiness of $H(0) = 0$

2) They can grade all the papers they are assigned, giving them a happiness of $H(g) - k$

3) They can grade i papers giving them a happiness of $(k-i)\div k \cdot H(G)-i$. This means that it is always worse to grade i, because happiness from grading i is equal to i times happiness for grading 0 plus i-k times happiness for grading k.

\subsection{Results}
Even though the students can communicate with one another, they will have no way to determine which paper is calibrated, and are thus best off grading all the papers.

\subsection{Problems}
The major problem with this method is the amount of work. The professor has to grade $\frac{n}{k}$ papers, which can be massive in a class of 1000+ students. For this reason a different mechanism was necessary.

\section{The Deduction Mechanism}
\label{sec:deduction}
In the new mechanism, a different strategy was created; one that would ideally work better than the previous ones.

\subsection{Mechanism}
For each assignment, a new assignment is created to evaluate the performance of the graders. Every student receives 2 papers from different people, so that each paper overlaps with one other person, and every paper is distributed twice. The student then chooses how many points to subtract, and writes a justification for each one of these points. Graders are then given a contribution score from 1 to -1. From each of the 2 assignments they grade, they get their points deducted / total points deducted-0.5. Then, if the original writers of the papers can appeal their grade if they are unhappy with it. The professor will grade the paper, and if any of the graders were wrong, they get a 0. To compute the final score, the grader's final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to H(the student's assigned grade). (Then the student's grade is converted from Happiness to an actual score).

See figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.

\subsection{Why it Works}
The graders have two choices, they can either grade the papers, or not grade them.

If the grader randomly takes off any points, the points will surely be refuted by the professor during the regrade, and the grader will get a 0 on the grading assignment.
If the grader gives it 100, he or she will get a 0 the grading assignment if his or her partner does not give 100. In the case of agreement, both graders get 50 on the grading assignment.
$$$$
If the grader does grade the paper, what score should he or she give it?

Therefore, it is in everyone's best interest to honestly grade the paper.

\subsection{Results}
Assuming that everyone acts in the dominant strategy behavior, the maximum work for teacher is 0, the maximum work done for students is 2. 
Because everyone honestly grades the papers, the maximum deviation is 0.
So, the objective function is 2, which is even better than the first mechanism.

\subsection{Problems}
Although the result that was produced for the previous mechanism is rather good, it encourages very harsh competition between students, and would make the classroom environment feel very negative. This means that finding a different solution to the same problem was necessary, in which students are placed in positive competition, instead of the negative one formed by trying to find the most mistakes

\section{The Flag Mechanism}
For the next mechanism, all of the assumptions were kept the same, and simply tried to find a way to better the feeling of negative competition.
\subsection{Mechanism}
Start by having each paper get graded by two people. Then, the original writer of this paper chooses which of the two grades he / she would like to have, and looks over the justifications for losing any points on both papers. If they see that any of these justifications are incorrect, they flag the paper and send it to the professor. Following this, the paper they chose to have is sent to a third party, who grades the paper, and checks if their grade is close to the one that was given to the paper. If it isn't, the paper is sent to the professor. After everything that needs to be flagged has been, the professor grades all the flagged papers, and rewards people who were correct with a 2 point bonus. If no papers from any group were flagged, every grader in that group gets two points. Final grades are whatever the person chose if there was no flagging, or whatever the professor gave them if there was.
\subsection{Why it Works}
To find out how efficient this mechanism is, two things needed to be analyzed:
1) Is everyone an honest flagger?
$$$$
2) Do the graders grade honestly
\subsubsection{Flagging}
There are two cases for this:

1) They guess a random score and try to flag everything

-In this case, the chance of gaining points is so low that it is negligible

2) They take the time to flag correctly

-In this case they could get 2 points back, so it is the most beneficial
\subsubsection{Grading}
Once again, there are two cases here: People grading, and people not grading

If people don't bother grading anything, what score should they give the paper?

-100 because anything lower than the actual score will be flagged by the writer, and because of useless justifications, they will lose points. 100 is the only score guaranteed to be greater than or equal to the correct score

Their happiness in this case will be 0, because they use no effort, but also have no chance of gaining points since their paper will definitely get flagged

The happiness of people who honestly grade, on the other hand, will be a +1 gain, because they use 1 unit of effort to grade and they get 2 units back guaranteed. This higher gain means that it is beneficial to grade honestly.

\subsection{Results}
Because everyone is honest, we can now analyze the score of the mechanism:

Maximum work done by one person: 3 (student who flags one paper and grades 2 others)

Maximum deviation: 1 (1 point gain for being a good grader)

Final score: 4

Although this is not as good as the previous mechanism, it is still an improvement because there is now positive competition instead of negative.
\subsection{Final Assumptions}
Now that we have reached a point far into the research, we are able to propose a model that accounts for a much more realistic and complex world:

\begin{enumerate}
\item When grading, $w_i=0 \oplus w_i=1$
\item For all students, $g_i \neq o_i$
\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral.
\item For a given student in $N$, that student has contact with all other students in $N$.
\end{enumerate}
Put simply:
\begin{enumerate}
\item Students cannot ``half bake''an assignment
\item Students can't always get the exact objective score
\item Students want good grades
\item Students don't like grading
\item Students are selfish
\item Doing work costs 1 unit of effort
\item Students are risk neutral with respect to happiness
\item All students can talk to each other
\end{enumerate}
\section{Illustrations}
{
\noindent
\begin{figure}
	\centering
		\label{fig:comparison}
		\includegraphics[width=\textwidth]{Comparison.eps}
		\caption {A comparison of mechanisms in terms of scalability, workload, and objective function.}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=\textwidth]{Flowchart-Calibration.eps}
		\caption {A flowchart of the Calibration Mechanism (section~\ref{sec:calibration}, page~\pageref{sec:calibration}) from the student perspective.\label{fig:calibration}}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=\textwidth]{Flowchart-Deduction.eps}
		\caption {A flowchart of the Deduction Mechanism (section~\ref{sec:deduction}, page~\pageref{sec:deduction}) from the student perspective.\label{fig:deduction}}
\end{figure}
}
\section{Conclusion}
In this research, we learned and established the validity of game theory and mathematically based models when solving complex problems involving human nature. Using this to answer the unanswered of how professors should go about grading the astronomically high number of papers submitted by students in the online courses known as MOOCs

@@

Even though the mechanisms are not truly valid, only one true question remains unanswered. This question being the question of what happens when our theory is introduced into the real world. As stated previously, to solve this question, we would prefer to create a system of implementation that would allows us to test our mechanisms.
\bibliography{bibliography}{}
\bibliographystyle{plain}
\end{document}

>>>>

\documentclass[12pt, Arial]{article}   	
\title{Teaching a Class to Grade Itself using Game Theory}
\author{Nick Kaashoek and William Wu}
\date{\today}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{wrapfig}
\usepackage[section]{placeins}
\usepackage{enumitem}
\setlength{\parindent}{15pt}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\begin{document}
\maketitle
\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole. Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started in May of 2012~\cite{canmoocsreducecc}. However, the MOOC's main importance comes from its scalability. MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: By the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofmoocs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

@@

\section{Materials and Methods}
\subsection{The Scenario}
In our trying to find a solution to the professor's problem, we consider the case of a single assignment. To apply them to an entire class, simply apply them to each assignment. In such a ``round''of grading, there are $n$ students, who each bring one ungraded paper to the professor. These ungraded papers are like the input for a function. Each of these papers, $i$ has an objective score $o_i\mid 0<o_i<100$. This is the score the professor would give out. Our mechanism then has the students grade the papers in a clever way and output the grades. We identify the students by an index $i$ from $1$ to $n$ and the professor as index $0$.
\subsection{Assumptions}
To create the models that are used to predict the behavior of the students, we use a set process every each time. To begin with, we create a set of assumptions. These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades. This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model. The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side. To begin with, a simple set of assumptions was created:
\begin{enumerate}[itemsep=0pt, parsep=0pt]
	\item Students want good grades
 	\item Doing work makes students unhappy
  	\item Students want to be happy
 	\item Students only care about their final happiness
  	\item The happiness of a student is only affected by their grade and the amount of work they do
\end{enumerate}
However, we wanted to create a mathematical solution, so these assumptions need to be changed into math terms. The result of this is as follows:
\begin{enumerate}[itemsep=0pt, parsep=0pt]
  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
  \item Students can grade others' work accurately (i.e they can find $o_i$) but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
  \item Students want to maximize their final happiness, expressed as $H(g)-W$
  \item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting x and y each with 50 percent chance, gives a happiness of 7.5).
  \item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It doesn't depend on the score of others
\end{enumerate}

@@

One advantage of this is that we can now address the fact that the above set of assumptions is rather simple and unrealistic, for instance assuming that every student is a perfect grader.
%Repeat above corrections%
\section{Results}
Once the rules and assumptions have been defined and the benchmark determined, different grading mechanisms can be created and tested. This is where mechanism design and game theory comes into play. Mechanism design is used to create a system that satisfies a set of constraints and achieves a certain purpose. Then, game theory is used to mathematically predict student behavior to benchmark such a system. Starting from the simplest and most obvious approaches, various mechanisms were created, tested, and refined upon in an iterative process that spanned several months. The end result is fairly complete, although there are still questions to be answered in future work.

\subsection{The Calibration Mechanism}

\subsubsection{Mechanism}
First, we design a mechanism that does extremely well in a model defined by our simple and unrealistic assumptions, which we used as a starting point.
\begin{definition}(Calibration Mechanism)
In this mechanism, the professor chooses one paper to grade, which he gives to every student, along with a second, ungraded paper. If the students fail to grade the paper the professor graded correctly, they get a 0. Otherwise they get the minimum of an arbitrary number $???$ and the grade their assigned grade.
\end{definition}
\begin{theorem}
With this mechanism, all students should behave honestly and the mechanism shoul output accurate grades while maintaining a low amount of per-person work.
\end{theorem}
\begin{proof}[Why this works]
See figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.

G is the maximum of \{ some minimum value, the assigned grade \}.
The happiness of one student grading one paper is equivalent to $\frac{H(G)+H(0)}{2}-1$ Because the students have a 0.5 chance of getting a 0, and a one-half chance of getting G.

If they grade both papers, their happiness will be equal to $H(G)-2$Because they spent two units of energy, and are guaranteed to get G.

If they grade neither then the happiness will be $H(0)$ Because they automatically get a 0, but spend no energy.

This means that if $H(G) - 2 > H(0)$, then student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, $H(???) > H(0) + 2$.
The teacher expends one unit of effort, each student spends 2, as long as the teacher set the minimum value high enough.
Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
So, maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
\end{proof}
\subsubsection{Benchmark}
The means that the value of the objective function in this case is 4, a very low value, because it is exactly the same as if we convinced every student to grade accurately grade 4 papers.

\subsubsection{Problems}
This mechanism is extremely simple, and relies on the unrealistic assumption that students are unable to communicate with each other. If they were able to, students would be able to figure out which paper is calibrated by checking which one they all share.

\subsection{Improved Calibration Mechanism}
\subsubsection{The Mechanism}
In the calibration mechanism, we assumed that students couldn't communicate with each other. For this mechanism, we relax this assumption, thus changing assumption number 11, which now reads as: \emph{All students are able to communicate with each other}
\begin{definition}(Improved Calibration Mechanism)
In this mechanism, we apply the calibration mechanism on a larger scale. Every student grades the papers of \emph{k} other students. The professor also grades every \emph{kth} paper, these are the calibrated papers. The same system for assigning grades is used as in the calibration mechanism.
\end{definition}
\begin{theorem}
In this mechanism, students will return accurate grades, even though they can communicate with each other.
\end{theorem}
\begin{proof}
In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other. As such, there are 3 options for the students. They can grade 0 papers, giving them a happiness of $H(0) = 0$ or grade all the papers they are assigned, giving them a happiness of $H(g) - k$ or they can grade $i$ papers giving them a happiness of $\frac{i}{k} \cdot H(G)-i$. This means that it is always worse to grade i, because happiness from grading i is equal to i times happiness for grading 0 plus i-k times happiness for grading k.

Even though the students can communicate with one another, they will have no way to determine which paper is calibrated because there are multiple calibrated papers that overlap, and are thus best off grading all the papers. As long as the minimum value is high enough, the papers will be accurately graded, as before.
\end{proof}
\subsubsection{Benchmark and Problems}
The maximum amount of work will be done by the professor, who has to grade $\frac{n}{k}$ papers, making the benchmark $\frac{n}{k}+4$, a potentially higher value than before. The huge problem with this is the high amount of work being done.

\subsection{The Deduction Mechanism}
With this mechanism, we aim to fix the faults of the previous mechanism while retaining the same set of assumptions. Other than reducing the workload, we aim to accomplish the same goals as the improved calibration mechanism.
\subsubsection{Mechanism}
See figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.
\begin{definition}(Deduction Mechanism)
In this mechanism, each paper is randomly assigned to 2 students. Students deduct as many points as they want, and write a justification for each of them. For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, sudent $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and j receives $\frac{x_j}{x_i + x_j}$. Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives an incorrect grader a 0. To compute the final score for a student, their final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to $H(g)$. (Then the student’s grade is converted from Happiness to an actual score).
\end{definition}
\begin{theorem}
The addition of the contribution score being added or subtraced should encourage graders to honestly grade papers, for fear of losing points and the possible reward.
\end{theorem}
\begin{proof}
The graders have two choices, they can either grade the papers, or not grade them.

If they take off any points, the points will surely be refuted by the professor during the regrade.
So if they take off any points, they will get a 0 on the grading assignment.
If the grader's give it 100, they might get 50 if the other grader also gives it 100. If he gives it anything else, the original grader will get 0.\\
If the grader does grade the paper, what score should he give it?

If the grader randomly takes off any points, the points will surely be refuted by the professor during the regrade, and the grader will get a 0 on the grading assignment.
If the grader gives it 100, he or she will get a 0 the grading assignment if his or her partner does not give 100. In the case of agreement, both graders get 50 on the grading assignment.\\
If the grader does grade the paper, what score should he or she give it?

Therefore, it is in everyone's best interest to honestly grade the paper.
\end{proof}
\subsection{Final Assumptions}
Now that we have reached a point far into the research, we have a model that accounts for a very realistic world view, however, the deduction mechanism still has some unrealistic parts, primarily the inablitity to deal with students who are incompetent graders. With this in mind, we designed a final set of assumptions that more effectively simulate a realistic world.

\begin{enumerate}[itemsep=0pt, parsep=0pt]
\item When grading, $w_i=0 \oplus w_i=1$
\item For all students, $g_i \neq o_i$
\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral.
\item For a given student in $N$, that student has contact with all other students in $N$.
\end{enumerate}
% Put simply:
% \begin{enumerate}[itemsep=0pt, parsep=0pt]
% \item Students cannot ``half bake''an assignment
% \item Students can't always get the exact objective score
% \item Students want good grades
% \item Students don't like grading
% \item Students are selfish
% \item Doing work costs 1 unit of effort
% \item Students are risk neutral with respect to happiness
% \item All students can talk to each other
% \end{enumerate}
\newpage
\section{Illustrations}
\begin{figure}[!ht]
	\centering
		\includegraphics[width=0.9\textwidth]{Comparison.eps}
		\caption {A comparison of mechanisms in terms of scalability, workload, and objective function.}
		\vspace{-100pt}
		\label{fig:Comparisongraph}
\end{figure}
\begin{figure}[!ht]
	\centering
		\includegraphics[width=0.75\textwidth]{Flowchart-Calibration.eps}
		\caption {A flowchart of the Calibration Mechanism from the student perspective.}
		\label{fig:calibration}
\end{figure}
\begin{figure}[!ht]
	\centering
		\includegraphics[width=0.75\textwidth]{Flowchart-Deduction.eps}
		\caption {A flowchart of the Deduction Mechanism from the student perspective.}
		\label{fig:deduction}
\end{figure}
\section{Discussion}
With this research, the goal was to create a mechanism that fulfilled our two goals; incentivizing students to play the ``game''the way they were meant to, and to efficiently and effectively grade the assignments of these students. Although our mechanisms are not truly realistic, the significance of them cannot be denied. The mechanisms created by the end of the research came very close to realism, with only one factor missing, and could still be implemented in a classroom environment where all students are capable of grading others assignments efficiently.

@@

Human judgment has always been superior to that of a machine, and this research continues to support that idea. As powerful as automated grading can be in practice, when it comes to theory, peer grading is simply more efficient. This means that with the right mechanism, such as the ones proposed by this research, so, in practice peer grading should be superior to automated grading. All in all, this research has opened doors for game theorists to make improvements to current grading schemes, and also provides mechanisms that are a distinct improvement over current peer and automated grading systems.

\section{Conclusion}
In this research, we learned and established the validity of game theory and mathematically based models when solving complex problems involving human nature. Using this to answer the unanswered of how professors should go about grading the astronomically high number of papers submitted by students in the online courses known as MOOCs

@@

Even though the mechanisms are not truly valid, only one true question remains unanswered. This question being the question of what happens when our theory is introduced into the real world. As stated previously, to solve this question, we would prefer to create a system of implementation that would allows us to test our mechanisms.
\newpage
\bibliography{bibliography}{}
\bibliographystyle{plain}
\end{document}
